NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-08-23 ms_nihao_budget.tex
discuss about the three most massive galaxies

As might be expected, haloes with the highest masses we study have
high baryon fractions with relatively  small scatter. As halo mass
decreases, the baryon fraction decreases and the scatter increases,
consistent with expectations from outflows driven by stellar
feedback. At the lowest halo masses we study, below $10^{10}\Msun$,
the scatter starts to decrease. By contrast the scatter in the stellar
mass fraction increases below this scale. Thus it seems unlikely that
stellar feedback is primarily responsible for the low baryon
fractions.  Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes.

>>>>

As might be expected, haloes with the highest masses we study have
high baryon fractions with relatively  small scatter. As halo mass
decreases, the baryon fraction decreases and the scatter increases,
consistent with expectations from outflows driven by stellar
feedback. At the lowest halo masses we study, below $10^{10}\Msun$,
the scatter starts to decrease. By contrast the scatter in the stellar
mass fraction increases below this scale. Thus it seems unlikely that
stellar feedback is primarily responsible for the low baryon
fractions.  Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes. 
{\bf Although the three most massive galaixes in NIHAO suite have fairly 
high stellar masses (see blue filled circles in Fig.~\ref{fig:budget}),
they don't have large deviations apart from the fitting baryon fraction, 
and in the comparason with FIRE (see Fig.~\ref{fig:fire_com}), these
three objects seem to hint the trend on massive galaxy end associated
with the data from \citet{Voort16}. Moreover, the fitting relation 
about the baryon fraction is not sensitive to these three most massive 
galaxies as well since they have equal weight with other more than 
80 galaxies to shape the fitting curve.}
